%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Embedded Systems Software Engineer} % Job title
    {Airbus via Critical Software} % Organization
    {Coimbra/Lisbon, Portugal} % Location
    {Jan. 2024 - Present} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Development and integration of \highlight{aviation critical embedded systems} for Airbus based on certification processes and industry standards (\highlight{DO-178C} and \highlight{DO-330});}
	\item {Performed \highlight{requirements specification}, \highlight{implementation (C)}, and \highlight{testing (Robot Framework)} following a \highlight{V Model} approach for \highlight{5 releases} one of them reaching SOI3 certification. Developed \highlight{6+ features} focused on data flow, storage and memory management;}
	\item {Collaborated with cross-functional teams (including client-side) for project alignment and compliance, having to adapt to new technical contexts;}
	\item {Used Jira for project management and task tracking, Git for source code management, and Jenkins for CI/CD. Developed Python/shell scripts to automate workflows. Used XML and JSON for environment configuration and tools integration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist Internship} % Job title
    {Take The Wind} % Organization
    {Coimbra, Portugal} % Location
    {Sep. 2022 - Sep. 2023} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Developed a \highlight{recommendation system prototype} to integrate their main product, Body Interact, with the goal of improving the users learning rate.}
     \item {Applied a agile software development cycle, created a Software Requirement Specification document, performed risk management and effort estimation.}
      \item {Performed \highlight{data preparation} with pandas, matplotlib and seaborn. Internally developed a user clinical competency-based evaluation algorithm resulting in \highlight{300+ user features} largely increasing the model training dataset.}
      \item {Created \highlight{cluster-based recommendations} using scikit-learn's models (K-Means, Hierachical, DBSCAN) with the aid of healthcare specialists.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist Researcher} % Job title
    {Centre for Informatics and Systems of the University of Coimbra} % Organization
    {Coimbra, Portugal} % Location
    {Mar. 2022 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tested tree-based models with encryption methods with a inovative confidential learning framework using scikit-learn and SEAL;}
        \item {Research paper accepted for presentation at the 27th IEEE Pacific Rim International Symposium on Dependable Computing in November 2022.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
